---
title: "General relativity in R"
output:
  github_document:
    pandoc_args: --webtex
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/schwarzschild)](https://cran.r-project.org/package=schwarzschild)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->


# Overview


The `schwarzschild` package creates a series of high-quality PDF
images showing different aspects of the physics of black holes.  The
software is available under the GPL and runs under the R programming
language. 

The package is intended as a resource for lecturers of general
relativity and it is envisaged that the diagrams be used as visual
teaching aids for understanding the Schwarzschild metric.  A number of
camera-ready PDF diagrams of black holes using a range of coordinate
systems are presented as examples of the software's functionality; the
software is extensively configurable to users' requirements.


# Installation

The package is not yet on CRAN.  To install the current development
version use `devtools`:

```
R> devtools::install_github("RobinHankin/schwarzschild", build_vignettes=TRUE)
```

And then to load the package use `library()`:

```{r,message=FALSE}
library("schwarzschild")
```

All PDF diagrams are created by `inst/maker.R` and a Makefile is
provided; altnernatively, the resulting PDF images are available at

[https://autuni-my.sharepoint.com/:f:/g/personal/rhankin_aut_ac_nz/EgX_IANsoOJDmTiH2i9_P20B6ksn9CMHf_TM31w5K3aITg?e=dPxAcp](https://autuni-my.sharepoint.com/:f:/g/personal/rhankin_aut_ac_nz/EgX_IANsoOJDmTiH2i9_P20B6ksn9CMHf_TM31w5K3aITg?e=dPxAcp)


# Further information

For more detail, see the package vignette; at the R prompt, type

`
vignette("schwarzschild")
`
 

